% ==============================================================================
% bibliography.tex — Список использованных источников
% Нумерация по порядку первого появления в тексте (ГОСТ Р 7.0.100-2018)
%
% Заголовок и добавление в оглавление выполняется автоматически
% средой thebibliography из G2-105.sty (\chapter*{\bibname})
% ==============================================================================

\begin{thebibliography}{34}

\bibitem{src:1}
BrightLocal. Local Business Discovery \& Trust Report 2023.~--- URL: \url{https://www.brightlocal.com/research/local-business-discovery-trust-report/} (дата обращения: 01.02.2026).

\bibitem{src:2}
BrightLocal. Local Consumer Review Survey 2024.~--- URL: \url{https://www.brightlocal.com/research/local-consumer-review-survey-2024/} (дата обращения: 01.02.2026).

\bibitem{src:3}
BrightLocal. Business Listings Trust Report 2021.~--- URL: \url{https://www.brightlocal.com/research/business-listings-trust-report/} (дата обращения: 01.02.2026).

\bibitem{src:4}
Google Business Profile Help. Edit your Business Profile.~--- URL: \url{https://support.google.com/business/answer/3039617} (дата обращения: 01.02.2026).

\bibitem{src:5}
Moz. The Impact of Local Business Reviews on Consumer Behavior / SEO Industry Report: The Habits of Review Readers.~--- URL: \url{https://moz.com/local-business-review-survey-report/habits-of-review-readers} (дата обращения: 01.02.2026).

\bibitem{src:6}
Bhardwaj~V. A Systematic Review of Robotic Process Automation in Business Operations: Contemporary Trends and Insights~// Journal of Intelligent Systems and Control.~--- 2023.~--- Т.~2, №~3.~--- DOI: 10.56578/jisc020304.

\bibitem{src:7}
El-Gharib~N.\,M., Amyot~D. Robotic Process Automation Using Process Mining~--- A Systematic Literature Review.~--- arXiv:2204.00751 (2022, revised 2023).~--- DOI: 10.48550/arXiv.2204.00751.

\bibitem{src:8}
IEEE/ISO/IEC 29148-2018: Systems and software engineering~--- Life cycle processes~--- Requirements engineering.~--- URL: \url{https://standards.ieee.org/standard/29148-2018.html} (дата обращения: 01.02.2026).

\bibitem{src:9}
ISO/IEC 25010:2023~--- Systems and software engineering~--- Systems and software Quality Requirements and Evaluation (SQuaRE)~--- Product quality model.~--- URL: \url{https://www.iso.org/standard/78176.html} (дата обращения: 01.02.2026).

\bibitem{src:10}
ISO/IEC 25010 (описание модели качества и характеристик).~--- URL: \url{https://iso25000.com/en/iso-25000-standards/iso-25010} (дата обращения: 01.02.2026).

\bibitem{src:11}
SendPulse Help Center. Deal pipeline basics.~--- URL: \url{https://sendpulse.com/knowledge-base/crm/pipeline} (дата обращения: 01.02.2026).

\bibitem{src:12}
OnePageCRM Help Center. Manage sales deals in OnePageCRM with Kanban view.~--- URL: \url{https://help.onepagecrm.com/article/642-pipeline-kanban-view} (дата обращения: 01.02.2026).

\bibitem{src:13}
Bitrix24 Helpdesk. Chat tracker.~--- URL: \url{https://helpdesk.bitrix24.com/open/14512848/} (дата обращения: 01.02.2026).

\bibitem{src:14}
SendPulse. CRM system (features).~--- URL: \url{https://sendpulse.com/features/crm} (дата обращения: 01.02.2026).


\bibitem{src:17}
Zhang~X. et al. A Survey of Multi-AI Agent Collaboration: Theories, Technologies and Applications~// Proceedings of DEAI~'25.~--- 2025.~--- URL: \url{https://dl.acm.org/doi/full/10.1145/3745238.3745531} (дата обращения: 01.02.2026).

\bibitem{src:18}
A2A Protocol. Agent2Agent (A2A) Protocol Specification (Release Candidate v1.0).~--- URL: \url{https://a2a-protocol.org/latest/specification/} (дата обращения: 01.02.2026).

\bibitem{src:19}
JSON-RPC Working Group. JSON-RPC 2.0 Specification.~--- URL: \url{https://www.jsonrpc.org/specification} (дата обращения: 01.02.2026).

\bibitem{src:20}
Model Context Protocol. Specification (2025-11-25).~--- URL: \url{https://modelcontextprotocol.io/specification/2025-11-25} (дата обращения: 01.02.2026).

\bibitem{src:21}
Telegram. Bot API.~--- URL: \url{https://core.telegram.org/bots/api} (дата обращения: 01.02.2026).


\bibitem{src:24}
Bitrix24. Contact Center (CRM): Free omnichannel contact center solution.~--- URL: \url{https://www.bitrix24.com/tools/crm/contact-center.php} (дата обращения: 01.02.2026).

\bibitem{src:25}
Bitrix24. CONTACT CENTER: All-In-One Communication Platform.~--- URL: \url{https://www.bitrix24.com/solutions/tool/contact_center.php} (дата обращения: 01.02.2026).

\bibitem{src:26}
Hootsuite. Social Media Calendar and Scheduler (Publishing).~--- URL: \url{https://www.hootsuite.com/platform/publishing} (дата обращения: 01.02.2026).

\bibitem{src:27}
Hootsuite Help Center. Bulk schedule your posts.~--- URL: \url{https://help.hootsuite.com/hc/en-us/articles/1260804249930-Bulk-schedule-your-posts} (дата обращения: 01.02.2026).

\bibitem{src:28}
Buffer. Social Media Scheduler \& Planner (Publish).~--- URL: \url{https://buffer.com/publish} (дата обращения: 01.02.2026).

\bibitem{src:29}
Buffer Help Center. Getting started with Buffer's publishing features.~--- URL: \url{https://support.buffer.com/article/600-getting-started-with-buffers-publishing-features} (дата обращения: 01.02.2026).

\bibitem{src:30}
SMMplanner. Automated social media posting.~--- URL: \url{https://page.smmplanner.io/en/} (дата обращения: 01.02.2026).

\bibitem{src:31}
SMMplanner. Content posting and re-poster for social media and messengers.~--- URL: \url{https://smmplanner.com/lang/en/repost} (дата обращения: 01.02.2026).

\bibitem{src:32}
YouScan. AI-powered Social Listening Platform with Visual Analysis (Product).~--- URL: \url{https://youscan.io/product/} (дата обращения: 01.02.2026).

\bibitem{src:33}
YouScan. Visual Insights: Next-generation social listening.~--- URL: \url{https://youscan.io/visual-insights/} (дата обращения: 01.02.2026).

\bibitem{src:34}
Kommo. Unified inbox.~--- URL: \url{https://www.kommo.com/unified-inbox/} (дата обращения: 01.02.2026).

\bibitem{src:35}
РОМИР. Геосервисы и поисковые системы~--- главные помощники россиян при выборе офлайн-заведений.~--- 2025-05-15.~--- URL: \url{https://romir.ru/studies/romir-geoservisy-i-poiskovye-sistemy--glavnye-pomoshchniki-rossiyan-pri-vybore-oflayn-zavedeniy} (дата обращения: 01.02.2026).

\bibitem{src:36}
Аналитический центр НАФИ. Рейтинг факторов, формирующих доверие продавцам в~e-commerce.~--- 2024-06-18.~--- URL: \url{https://nafi.ru/analytics/reyting-faktorov-formiruyushchikh-doverie-prodavtsam-v-e-commerce/} (дата обращения: 01.02.2026).

\end{thebibliography}
